{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2018-01-18 thesis/landslide.tex
improve dpor bgnd; add some static landslide configs

\subsection{Running Landslide through Quicksand}

@@

\begin{itemize}
	\item {\tt -C}: enable ``control experiment'' mode, i.e., run only 1 instance of Landslide, with all (non-data-race) preemption points enabled in advance
		% TODO: put a section reference here
	\item {\tt -I}: enable Iterative Context Bounding (requires {\tt -C}, although future work may relax this restriction);
		this generally causes bugs to be found faster should they exist, but degrades completion time
	\item {\tt -0}: enable Preempt-Everywhere mode (see \sect{\ref{sec:quicksand-eval}}, requires {\tt -C})
	\item {\tt -H}: use Limited Happens-Before for data-race analysis (see \sect{\ref{sec:background-hb}})
		(default for Pebbles kernelspace mode)
	\item {\tt -V}: use vector-clock-based Pure Happens-Before for data-race analysis (see \sect{\ref{sec:background-hb}})
		(default for P2 userspace and Pintos modes)
	\item {\tt -X}: support transactional memory (see Chapter~\ref{chap:tm})
		% TODO: make a more specific section reference
	\item {\tt -A}: support multiple abort codes during transaction failure (see Chapter~\ref{chap:tm});
		required for testing programs which behave differently under different abort circumstances,
		but impacts the state space size
	\item {\tt -P}: support Pintos architecture (enabled automatically when {\tt pintos-setup.sh} is run)
	\item {\tt -4}: support Pebbles architecture (enabled automatically when {\tt p2-setup.sh} is run)
	\item {\tt -e ETAFACTOR}: configure heuristic state space ETA deferring factor (described in detail in {\tt id/option.c})
	\item {\tt -E ETATHRESH}: configure heuristic threshold of state space progress for judging ETA stability (described in detail in {\tt id/option.c})
\end{itemize}

@@

\subsubsection{Dynamic configuration options}
First, the following options may be changed without triggering a recompile of Landslide.

\begin{itemize}
	\item {\tt within\_function} % TODO
	\item {\tt within\_user\_function} - as above but finds the function in the userspace test program rather than the kernel code.
	\item {\tt without\_function} % TODO
	\item {\tt without\_user\_function} - difference to one above same as stated two above.
	\item {\tt data\_race ADDR TID LAST\_CALL CURRENT\_SYSCALL} - specifies a data-race preemption point.
		\begin{itemize}
			\item {\tt ADDR} shall be the code address (in hex) of the racing address,
			{\em before} the execution of which a preemption will be issued.
			\item {\tt TID} indicates a thread ID required to be running for this data race.
				To specify data race PPs across all threads at once, set {\tt FILTER\_DRS\_BY\_TID=0} (see next section).
			\item {\tt LAST\_CALL} indicates a code address required to be the site of the last {\tt call} instruction executed
				(similar to specifying a stack trace, but using a full stack trace here degrades performance too much),
				or 0 to not use this feature.
				From personal experience I found this option rather useless and recommend always supplying 0.
				% TODO: fix this section ref
				For further discussion see \sect{\ref{sec:quicksand-pps}}.
			\item {\tt CURRENT\_SYSCALL} indicates the system call number if a user-space data race comes from within a kernel system call which accesses user memory (Pebbles only).
				Usually 0 (i.e., not in kernel code) but {\tt deschedule}'s system call number is common as well.
		\end{itemize}
	\item {\tt input\_pipe FILENAME} - FIFO file used for receiving messages from Quicksand (e.g. to suspend or resume execution).
		Requires {\tt id\_magic} option to be set (next section below).
		The odds a human user will find success using this option by hand are infinitesimal.
	\item {\tt output\_pipe FILENAME} - as above but for sending messages.
\end{itemize}

@@

\begin{itemize}
	\item {\tt FILTER\_DRS\_BY\_TID=1} - configures whether to use the {\tt TID} parameter of {\tt data\_race} described above.
	\item % TODO moar
\end{itemize}

@@

\subsection{Scheduler}
\subsection{Memory analysis}
\subsection{Machine state manipulation}
\subsection{State space traversal}
% time travel, explore, arbiter
\subsection{Debugging output}
% symtable stuff goes here
% stack tracing goes here
% foundabug goes here
\subsection{Pebbles-specific features}
\subsection{Pintos-specific features}
\subsection{Handy scripts}
\label{sec:landslide-glue}

@@

\subsection{Kernel annotations}
\subsection{Bug identification}
\subsection{Data race analysis}
\subsection{Preemption point identification}
\subsection{State space estimation}
\subsection{Dynamic Partial Order Reduction}
\subsection{Heuristic loop, deadlock, and synchronization detection}

>>>>

\subsection{Running Landslide through Quicksand}
\label{sec:landslide-quicksand-options}

@@

\begin{itemize}
	\item {\tt -C}: enable ``control experiment'' mode, i.e., run only 1 instance of Landslide, with all (non-data-race) preemption points enabled in advance
		% TODO: put a section reference here
	\item {\tt -I}: enable Iterative Context Bounding (requires {\tt -C}, although future work may relax this restriction);
		this generally causes bugs to be found faster should they exist, but degrades completion time
		(\sect{\ref{sec:landslide-icb}})
	\item {\tt -0}: enable Preempt-Everywhere mode (\sect{\ref{sec:quicksand-eval}}, requires {\tt -C})
	\item {\tt -H}: use Limited Happens-Before for data-race analysis (\sect{\ref{sec:background-hb}})
		(default for Pebbles kernelspace mode)
	\item {\tt -V}: use vector-clock-based Pure Happens-Before for data-race analysis (\sect{\ref{sec:background-hb}})
		(default for P2 userspace and Pintos modes)
	\item {\tt -X}: support transactional memory (Chapter~\ref{chap:tm})
		% TODO: make a more specific section reference
	\item {\tt -A}: support multiple abort codes during transaction failure (Chapter~\ref{chap:tm});
		required for testing programs which behave differently under different abort circumstances,
		but impacts the state space size
	\item {\tt -P}: support Pintos architecture (enabled automatically when {\tt pintos-setup.sh} is run)
	\item {\tt -4}: support Pebbles architecture (enabled automatically when {\tt p2-setup.sh} is run)
	\item {\tt -e ETAFACTOR}: configure heuristic state space ETA deferring factor (described in detail in {\tt id/option.c})
	\item {\tt -E ETATHRESH}: configure heuristic threshold of state space progress for judging ETA stability (described in detail in {\tt id/option.c})
\end{itemize}

@@

\subsubsection{Dynamic configuration options}
First, the following options may be changed without triggering a recompile of Landslide.
They are implemented as bash functions defined in {\tt pebsim/build.sh}.

\begin{itemize}
	\item {\tt within\_function FUNC} - adds {\tt FUNC} to a whitelist of functions required to appear in the current stack trace before identifying a preemption point (see \sect{\ref{sec:landslide-pps}})
	\item {\tt without\_function FUNC} - as above, but a blacklist instead of a whitelist
	\item {\tt within\_user\_function FUNC} - as two above but finds the function in the userspace test program rather than the kernel code.
	\item {\tt without\_user\_function FUNC} - difference to two above same as stated one above.
	\item {\tt data\_race ADDR TID LAST\_CALL CURRENT\_SYSCALL} - specifies a data-race preemption point.
		\begin{itemize}
			\item {\tt ADDR} shall be the code address (in hex) of the racing address,
			{\em before} the execution of which a preemption will be issued.
			\item {\tt TID} indicates a thread ID required to be running for this data race.
				To specify data race PPs across all threads at once, set {\tt FILTER\_DRS\_BY\_TID=0} (see next section).
			\item {\tt LAST\_CALL} indicates a code address required to be the site of the last {\tt call} instruction executed
				(similar to specifying a stack trace, but using a full stack trace here degrades performance too much),
				or 0 to not use this feature.
				From personal experience I found this option rather useless and recommend always supplying 0.
				% TODO: fix this section ref
				For further discussion see \sect{\ref{sec:quicksand-pps}}.
			\item {\tt CURRENT\_SYSCALL} indicates the system call number if a user-space data race comes from within a kernel system call which accesses user memory (Pebbles only).
				Usually 0 (i.e., not in kernel code) but {\tt deschedule}'s system call number is common as well.
		\end{itemize}
	\item {\tt input\_pipe FILENAME} - FIFO file used for receiving messages from Quicksand (e.g. to suspend or resume execution).
		Requires {\tt id\_magic} option to be set (next section below).
		The odds that a human user will find spiritual enlightenment through using this option by hand are infinitesimal.
	\item {\tt output\_pipe FILENAME} - as above but for sending messages.
\end{itemize}

@@

\begin{itemize}
	\item {\tt TEST\_CASE} - configure the name of the test program to run (mandatory; no default)
	\item {\tt VERBOSE=0} - enable more verbose output
	\item {\tt FILTER\_DRS\_BY\_TID=1} - configures whether to use the {\tt TID} parameter of {\tt data\_race} described above.
	\item {\tt ICB=0} - enable Iterative Context Bounding (\sect{\ref{sec:landslide-icb}});
		corresponds to {\tt -I} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt PREEMPT\_EVERYWHERE=0} - enable Preempt-Everywhere mode (\sect{\ref{sec:quicksand-eval}});
		corresponds to {\tt -0} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt PURE\_HAPPENS\_BEFORE=1} - select Pure Happens-Before (1) or Limited Happens-Before (2) (\sect{\ref{sec:background-hb}});
		corresponds to {\tt -V}/{\tt -H} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item % TODO moar
\end{itemize}

@@

\subsection{Scheduler}
\subsection{Memory analysis}
\subsection{Machine state manipulation}
\subsection{State space traversal}
% time travel, explore, arbiter
\subsection{Bug-finding output}
% symtable stuff goes here
% stack tracing goes here
% foundabug goes here
\subsection{Pebbles-specific features}
\subsection{Pintos-specific features}
\subsection{Handy scripts}
\label{sec:landslide-glue}

@@

\subsection{Kernel annotations}
\subsection{Bug identification}
\subsection{Data race analysis}
\subsection{Preemption point identification}
\label{sec:landslide-pps}
% TODO: talk about how w/in func and w/out func are processed
\subsection{State space estimation}
\subsection{Dynamic Partial Order Reduction}
\label{sec:landslide-dpor}
\subsection{Iterative Context Bounding}
\label{sec:landslide-icb}
\subsection{Heuristic loop, deadlock, and synchronization detection}
